% Thesis Abstract
% ---------------------------------------------------------------------------------------------------------------
\prefacesection{Abstract}

The growth that have had the operative system Android is remarkable. There are more than one million applications availables on Google Play and every month these numbers are increasing. Consequently, the development process of Android applications have gained a lot of importance.

The goal of this work is do research and compare tools that help to improve the development process of Android applications, and provide future developers with some guidance that let them take better decisions during a project.

The most common problems for Android developers are related with the fragmentation in two levels, software and hardware. Also there is the distribution of pre-release versions before launching and handling crashes. Have been studied and compared tools to solve and mitigate these problems, classified in the following categories: testing, beta distribution and crash reports. The comparison parameters used to help the developers to decide what tool is best suited for their application are: price, usability, maturity, support for multiplatforms, between others.

The tools that are more suited to the needs of an application at the official store of Google, Seahorse, were implemented to validate its features.

\textbf{Keywords:} Android, Mobile Applications, Testing, Distribution, Crash Reports.
% ---------------------------------------------------------------------------------------------------------------
